---
title: "Wweek_5_Exploratory_Data_Analysis_Graphics_Labs"
author: "Nitie"
date: "9/21/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

```{r}
library(plotly)
library(ggplot2)
library(dplyr)
library(VennDiagram)
library(ggbeeswarm)
```


```{r}
#Read in dataset
```
#control option M= commit
## Including Plots

You can also embed plots, for example:
1.Read the file diabetes2.csv into a dataframe named diab.
```{r}
diab<-read.csv(file = "./data/diabetes2.csv",header = T, sep = ",")
```
2.EDA: Calculate summary statistics on diab and identify which variables seem to have invalid
data in need of cleaning.
```{r}
Sum<-diab
str(diab)
freq_insu<- ggplot(diab, aes(insu))+ geom_histogram(color = "black", fill = "light blue", binwidth = 0.02)
freq_insu
```
3. EDA: Plot the frequency distributions of all variables in diab and identify which variables seem to have invalid data in need of cleaning. Reconcile differences in #2 and #3, if there are any.
```{r}
table(diab$preg)
table(diab$plas)
table(diab$pres)
table(diab$skin)
table(diab$insu)
table(diab$mass)
table(diab$pedi)
table(diab$age)
table(diab$class)
```
4. For the variable insu produce a new variable of logical that has the value TRUE at any position in the vector diab$insu.
```{r}
diab$insu[diab$insu==0]<-"NA"
hist(diab$insu)
```
5a. For the variable pres (ie: blood pressure) produce a new variable of logical that has the value ZOMBIE at any position in the vector diab$pres where the blood pressure is that of a zombie rather than that of a human. Hint: zombies do not have a heartbeat – what BP results from no heartbeat?
```{r}
```{r}

```

```
5b. For the variable pres use a logical expression from #4 to take a slice of the vector diab$pres. This slice will contain all the elements of diab$pres that need to be replaced with NA.
```{r}

```
6. For the variable pres use your slice of diab$pres from #5 to replace the values that should be NA with the value NA.
Hint: one way is to use something like this, filling in with your logical expression from #4 and #5: diab$pres[<logical expression>] <- NA
```{r}

```
7. For the variable skin (ie: measure of skin fold thickness at triceps) use a logical expression to take a slice of the vector diab$skin. This slice will contain all the elements of diab$skin that need to be replaced with NA.